---
title: "Workspace"
author: "Zoe Webb"
date: "2022-11-01"
output: html_document
---
##Basic Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r Packages}
#install packages
install.packages(
  c("tidyverse", 
    "tidyselect", 
    "cowplot", 
    "googleway", 
    "ggplot2", 
    "ggrepel", 
    "ggspatial", 
    "lwgeom", 
    "sf", 
    "rnaturalearth",
    "rnaturalearthdata", 
    "ggthemes", 
    "jpeg", 
    "png")
  )

#load packages
library(tidyverse)
library(tidyselect)
library(cowplot)
library(googleway)
library(ggplot2)
library(ggrepel)
library(ggspatial)
library(lwgeom)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggthemes)
library(jpeg)
library(png)

#create primary dataset
world <- ne_countries(scale = "medium", 
                      returnclass = "sf")
class(world)
```
```{r Snip dataset}
world_small <- world %>%
  select(sovereignt, type, admin, name, name_long, formal_en, postal)
```
```{r Test map}
world_small %>%
  ggplot() +
  geom_sf()
```

**Variables to change/make**
name_long -> name_formal
name -> name (Standardized name)
name_alt -> Alternative name
un_name + UN recognized name
un_recognized = Boolean value of UN recognition
type -> type (UN recognition + Dependency status)
world_bank, european_union, NATO, etc = Boolean value of membership of various organizations

I'm going to use the postal code to standardize my joins

**How to export data**
This can then be imported into excel or google sheets
```{r Remove Geom}
world_no_geom <- dplyr::select(as.data.frame(world), -geometry)
```
```{r Export dataset}
write.table(world_improved, file = "world_improved0.1.txt", append = TRUE, quote = TRUE, sep = ",",
            eol = "\n", na = "NA", dec = ".", row.names = FALSE,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```

```{r N/A to *n/a*}
world_zoe <- World_Zoe %>%
  mutate(
    across(
      everything(), ~replace(., . %in% c("N.A.", "NA", "N/A", ""), NA)))
```

```{r Joining sets}
world_new <- world_small %>%
  left_join(world_zoe, 
            world_small, 
            by = "postal")
```

```{r Remove old data}
world_improved <- world
```

```{r Check column types}
str(world)
```